Reanalysis Step 1: Data Preparation

### 2025-08-17 reanalysis-1-data_preparation.qmd
set mirror & seed
parameterize test/final, print out analysius model, consistent seeds
cleanup

```{r setup}
#| include: false
# Setup analysis environment
source("dependencies.R")
setup_analysis()
```

@@

## Next Steps

1. **Multiple Imputation** (`reanalysis-2-multiple_imputation.qmd`): Impute missing values in covariates
2. **Propensity Score Analysis** (`reanalysis-3-propensity_scores.qmd`): Calculate PS using various methods on imputed datasets
3. **Outcome Analysis** (`reanalysis-4-outcome_analysis.qmd`): Fit outcome models and pool results
4. **Sensitivity Analysis** (`reanalysis-5-sensitivity.qmd`): Compare complete case vs imputed results

>>>>

```{r setup}
#| include: false
# Setup analysis environment (includes seed setting)
source("dependencies.R")
setup_analysis(seed = 2025)
```

@@
